upwell_IDX

### 2020-04-23 upwell_IDX.Rmd
edits

library(circular)
## devtools::install_github("robwschlegel/coastR")
library(gridExtra)
library(geosphere)
library(tidyverse)
library(heatwaveR)
library(coastR)
```

@@

save(wind_daily, file = "Data/wind_daily.RData") 
```

>>>>

library(circular)
library(foehnix)
## devtools::install_github("robwschlegel/coastR")
## devtools::install_github("retostauffer/Rfoehnix")
library(gridExtra)
library(geosphere)
library(tidyverse)
library(heatwaveR)
library(coastR)
```

@@

library(openair)
wind_daily_speed <- timeAverage(wind_data, avg.time = "day")
# save(wind_daily, file = "Data/wind_daily.RData")

#Convert Wind Speed and Wind Direction to u/v Wind Components 
# Then get the daily average and then convert it back?
# https://rdrr.io/github/retostauffer/Rfoehnix/man/ddff2uv.html
# Use with zoo
library("zoo")
set.seed(100)
Sys.setenv("TZ" = "UTC")
## Calculate dd/ff
wind_data <- wind_data %>% 
  rename(dd = dir,
         ff = speed)

uv <- ddff2uv(wind_data)
```
